term papaer 2

### 2024-02-13 outputs/paper/paper.qmd

```{r setup}
#| echo: false
#| message: false
#| warning: false
# install.packages('readr')
install.packages("here")
install.packages("dplyr") 
install.packages("tidyverse")
installed.packages("ggplot2")
# install.packages("knitr")

library(here)
library(dplyr)
library(tidyverse)
library(knitr)
library(rdrobust)
library(ggplot2)

data_path <- here("outputs", "edited_data", "election_cleaned.csv")
election <- read.csv(data_path)
```

@@

## Source

@@

It uses datasets constructed from four data sources: 1) Brazil municipal election data (Tribunal Superior Eleitoral, 1996-2016); 2) Brazil demographic censuses (Instituto Brasileiro de Geografia e Estatística, 1980, 1991, 2000, 2010); 3) Brazil school census (Ministério da Educação, 1997-2016); and 4) nighttime lights (National Oceanic and Atmospheric Administration, 1997-2016a,-).

@@

这里需要被使用到的Data/文件/数据的名字，参考教授example里的2022年第一个例子，2.2.1部分 \# Results
\renewcommand{\arraystretch}{2}
# Result

@@

table pie chart
```{r}
#| label: fig-statements
#| fig-cap: "University degree"
#| echo: false
#| message: false
#| warning: false

p <- ggplot(data = election, aes(x = tse_code, y = edu_univ)) +
  geom_point(color = "blue") +  # Scatter plot points
  labs(x = "Number of registered voters", y = "University degree \n (fraction")
p + geom_smooth(method = "lm", color = "red")
```

>>>>

```{r setup}
#| echo: false
#| message: false
#| warning: false
# install.packages('readr')
install.packages("here")
install.packages("dplyr") 
install.packages("tidyr") 
install.packages("tidyverse")
installed.packages("ggplot2")
install.packages("kableExtra") 
# install.packages("knitr")

library(here)
library(dplyr)
library(tidyverse)
library(knitr)
library(rdrobust)
library(ggplot2)
library(tidyr) 
library(kableExtra)

data_path <- here("outputs", "edited_data", "election_cleaned.csv")
election <- read.csv(data_path)
data_path2 <- here("outputs", "edited_data", "schools.csv") 
school <- read.csv(data_path2)
```

@@

@@

It uses data sets constructed from four data sources: 1) Brazil municipal election data (Tribunal Superior Eleitoral, 1996-2016); 2) Brazil demographic censuses (Institute Brasileiro de Geografia e Estatística, 1980, 1991, 2000, 2010); 3) Brazil school census (Ministério da Educação, 1997-2016); and 4) nighttime lights (National Oceanic and Atmospheric Administration, 1997-2016a,-).

@@

这里需要被使用到的Data/文件/数据的名字，参考教授example里的2022年第一个例子，2.2.1部分 \# Results
\renewcommand{\arraystretch}{2}

# Result

@@

table pie chart

```{r}
#| label: fig-hist
#| fig-cap: histogram
#| echo: false
#| message: false
#| warning: false
data_long <- pivot_longer(election, cols = c("inc_0_50_post", "inc_post", "unempl_post"), 
                          names_to = "Variable", values_to = "Value")

ggplot(data_long, aes(x=Value, fill=Variable)) + 
  geom_histogram(position="dodge", binwidth=1) + 
  facet_wrap(~ Variable, scales = "free_x") + 
  theme_minimal() + 
  ggtitle("hist") +
  xlab("Value") +
  ylab("Frequency") +
  scale_fill_manual(values = c("inc_0_50_post" = "blue", "inc_post" = "red", "unempl_post" = "green"))
```

```{r}
#| label: fig-hist
#| tbl-cap: histogram
#| echo: false
#| message: false
#| warning: false

```{r}
#| label: fig-model
#| fig-cap: "umemployment rate Vs low income rate"
#| echo: false
#| message: false
#| warning: false

cutoff_value <-60000
school$cutoff_side <- ifelse(school$tse_code < cutoff_value, "Below", "Above")

p <- ggplot(data = school, aes(x = tse_code, y = MAT_DROP_mean)) +
  geom_point(color = "blue") +  
  labs(x = "Number of registered voters", y = "Drop-our rate") +
  geom_vline(xintercept = cutoff_value, linetype = "dashed", color = "black") + # Cutoff line
  geom_smooth(data = subset(election, tse_code < cutoff_value), 
              aes(x = tse_code, y = inc_0_50_post), 
              method = "lm", color = "red") + 
  geom_smooth(data = subset(election, tse_code >= cutoff_value), 
              aes(x = tse_code, y = inc_0_50_post), 
              method = "lm", color = "red") 
p 
```
